Using Semantic Similarity to Assist Assessing MCR Comment Usefulness

### 2014-07-26 sections/methods.tex
Merged Case Study Design and Case Study Results sections
I’ve gone as far as I can for now. Please add the actual results so I
can make sure we present them clearly.

\subsubsection{Ground-Truth Data Preparation}
To prepare ground-truth data, a team of three experienced developers independently read comments and manually assessed them useful or useless. The assessors were asked to answer for each comment the question ``Does this comment technically contribute to its proposed change?''. Then, the assessors cast their vote as \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless.  Comments with three \texttt{YES} votes are classified as \textbf{useful} comments and comments with three \texttt{NO} votes are \textbf{useless}. Comments lacking unanimity (i.e. one or two \texttt{YES} votes are deemed \textbf{unclear} and without confident usefulness.

@@

\noindent \textbf{RQ1: Is semantic similarity a good indicator of MCR comment usefulness?}\\
\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection. Then, we used these comments for both the training and test data set for our approach to determine its effectiveness. We also determined the robustness of our approach using cross validation. We randomly selected 90\% of 320 comments for training set and 10\% for test set.
The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.

@@

Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).

@@

\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set. We then used these thresholds to classify the rest of comments. A statical analysis was performed to understand the impact of useful discussion to software quality.

\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
\indent

>>>>

\subsubsection{Ground-Truth Data Preparation}
To prepare ground-truth data, a team of three experienced developers independently read comments and manually assessed them useful or useless. The assessors were asked to answer for each comment the question ``Does this comment technically contribute to its proposed change?''. Then, the assessors cast their vote as \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless.  Comments with three \texttt{YES} votes are classified as \textbf{useful} comments and comments with three \texttt{NO} votes are \textbf{useless}. Comments lacking unanimity i.e. one or two \texttt{YES} votes are deemed \textbf{unclear} and not confidently useful or useless.

@@

\dan{Why is this a separate section? Either the actual results should deb discussed here or this should be integrated into the results section.}

\noindent \textbf{RQ1: Is semantic similarity a good indicator of MCR comment usefulness?}\\
\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection. Then, we used these comments for both the training and test data set for our approach to determine its effectiveness. We also determined the effectiveness of our approach using bootstrapping cross validation. We randomly selected 90\% of 320 comments for training set and 10\% for the validation set.
The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times to estimate the mean and variance of the performance.

@@

Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).
\dan{I thought we changed this! It would be bad if we didn't. Let me know what the actual situation is here.}

@@

\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set. We then used these thresholds to classify the rest of comments. A statical analysis was performed to understand the impact of useful discussion to software quality.
\dan{results?}

\noindent \textbf{RQ3:  Is semantic similarity classification cost-efficient, assur- able, and scalable?}\\
\indent
\dan{results?}

### 2014-07-26 sections/results.tex
Merged Case Study Design and Case Study Results sections
I’ve gone as far as I can for now. Please add the actual results so I
can make sure we present them clearly.

\section{Case Study Results}
\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}
Table \ref{tb:datastatistic} summarizes data set we used for this study after preparation.
From 72,484 comments of 6,605 reviews with its commit messages extracted from raw data set, there are 10,670 (15\%) of comments are written by reviewers while 85\% of comments are automatically generated by Gerrit system and integration bots.

\begin{table}[!h]
\caption{A summary data sets and some statistics.}
\centering
\small
\begin{tabular}{ccc}
\hline
& Total Number & Percentage \\ \hline \hline
Commit Messages & 6,605 &  -  \\ \hline
All Comments & 72,484& - \\ \hline
Reviewers Messages & 10,670 & 15\% \\ \hline
Automated Messages. & 61,814 & 85\% \\ \hline

@@

@@

\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}

From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from \TODO{.......}. \pick{We cannot brute force for every floating number. How did we calculate this?} Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score. \pick{I used dummy results. Please change it} \pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}

@@

\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
\pick{The questions: How many \% automatic / useful/ useless/ unclear messages for each reviews? Does these numbers have a relationship with factor of code review (e.g. reviewing time)?}

@@

\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\

>>>>

\section{Case Study}
%\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject \texttt{qtbase} project. From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.

\subsection{Data Preparation}
We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we first processed the commit message and comments as follows:

\subsubsection{Automatically generated messages removal}
In Gerrit, the comments are composed of comment messages from reviewers and automated messages. These automatic messages are generated by Gerrit and the integration system to record activities. For example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}. Since these messages are generally recored keeping, they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition. In practice they are not considered in code review. They are easily determined as useless by our method and would artificially improve our classification performance. We identified these automatic messages using regular expressions and selecting frequently appeared patterns of messages.

\subsubsection{Data Preprocessing}
 As is customary for VSM processing we extracted semantic words from commit messages and comment messages before converting to vector. For each message, we removed all punctuation signs, digits, and common words (e.g. a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}. We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.

Table \ref{tb:datastatistic} summarizes data set we used for this study after preparation.

\begin{table}[!h]
\caption{A summary data sets and some statistics.}
\centering
\small
\begin{tabular}{ccc}
\hline
& Total Number & Percentage \\ \hline \hline
Commit Messages & 6,605 &  -  \\ \hline
All Comments & 72,484& - \\ \hline
Reviewers Comments & 10,670 & 15\% \\ \hline
Automated Comments & 61,814 & 85\% \\ \hline

@@

\subsection{Research Questions}

@@

\noindent \textbf{RQ1: Is semantic similarity a good indicator of MCR comment usefulness?}\\
\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection. Then, we used these comments for both the training and test data set for our approach to determine its effectiveness. We also determined the effectiveness of our approach using bootstrapping cross validation. We randomly selected 90\% of 320 comments for training set and 10\% for the validation set.
The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times to estimate the mean and variance of the performance.

\dan{What what the effort in person-hours for this?}

Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).
\dan{I thought we changed this! It would be bad if we didn't. Let me know what the actual situation is here.}

From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from \TODO{.......}. 
\pick{We cannot brute force for every floating number. How did we calculate this?} 
\dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}

Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score. \pick{I used dummy results. Please change it} \pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}

@@

\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set. We then used these thresholds to classify the rest of comments. A statical analysis was performed to understand the impact of useful discussion to software quality.
\pick{The questions: How many \% automatic / useful/ useless/ unclear messages for each reviews? Does these numbers have a relationship with factor of code review (e.g. reviewing time)?}

@@

\noindent \textbf{RQ3: Is semantic similarity classification cost-efficient, assur- able, and scalable?}\\
